Stock enhancement undermines community stability

### 2022-02-02 rmd/figures.Rmd
edit: figure caption

**Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics. In A and B, panels and colors distinguish response variables and species groups, respectively. (A) Theoretical predictions. Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and their 95% confidence intervals. Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`. (B) Empirical evidence. Dots represent observed values in 31 watersheds. Site-level values were averaged in each watershed (geometric mean). Lines are predicted values of regression models, and line types corresponds to posterior probabilities of regression coefficients. See Tables S8-10 for full statistics. (C) Map of sampling sites (black dots) in Hokkaido, Japan. (D) Example of an protected watershed (Okushibetsu). (E) Masu salmon *Oncorhynchus masou masou*. Photo credit: Akira Terui.

>>>>

**Figure 1** Theory and empirical observations agree that stock enhancement destabilizes community dynamics. In A and B, panels and colors distinguish response variables and species groups. (A) Theoretical predictions. Dots represent individual simulation replicates, and lines and shades are loess curves fitted to simulated data and 95% confidence intervals. Parameters used in this simulation are: intrinsic growth rate of the enhanced species $r_1=$ `r unique(df0$r1)`, average interspecific competition $\bar{\alpha}=$ `r unique(df0$alpha)`, carrying capacity $K=$ `r unique(df0$k)`, environmental stochasticity $\sigma_{\epsilon}=$ `r unique(df0$sd_env)`, relative fitness of captive-bred individuals $f_R=$ `r unique(df0$phi)`. (B) Empirical evidence. Dots represent geometric means of site-level observations in 31 watersheds. Lines are the predicted values of the regression models, and line types correspond to the coefficient's posterior probabilities. See Tables S8-10 for full statistics. (C) Map of sampling sites (black dots) in Hokkaido, Japan. (D) Example of a protected watershed (Okushibetsu). (E) Masu salmon *Oncorhynchus masou masou*. Photo credit: Akira Terui.
